---
title: "**Presentations in R with revealjs**"
author: "*Roberto Jesús Alcaraz Molina*"
date: "26/02/2021"
output: 
  revealjs::revealjs_presentation:
    theme: serif
    center: T
    self_contained: false
    highlight: kate
    transition: convex
    css: styles.css
    reveal_options:
      slideNumber: true
---

```{r, echo=F}
pacman::p_load(Stat2Data, knitr, dplyr, patchwork, ggplot2, ggpubr, plotly, htmlwidgets)
# install_github("thomasp85/patchwork")
```

# Stat2Data Package

In the following presentation we will do a simple analysis of the ``ThreeCars`` data set from the ``Stat2Data`` package, which compare prices for Porsche, Jaguar, and BMW cars offered for sale at an internet site.

Student project data collected from autotrader.com in Spring 2007.

## Three Cars data set

It is a data set with 90 observations on the following 8 variables:

<ul>
<li class="fragment fade-in" data-fragment-index="1">``CarType``: BMW, Jaguar, or Porsche.</li>
<li class="fragment fade-in" data-fragment-index="2">``Price``: Asking price (in $1,000's).</li>
<li class="fragment fade-in" data-fragment-index="3">``Age``: Age of the car (in years).</li>
<li class="fragment fade-in" data-fragment-index="4">``Mileage``: Previous miles driven (in 1,000's).</li>
<li class="fragment fade-in" data-fragment-index="5">``Car``: 0=Porsche, 1=Jaguar and 2=BMW. </li>
<li class="fragment fade-in" data-fragment-index="6">``Porsche``: Indicator with 1=Porsche and 0=otherwise.</li>
<li class="fragment fade-in" data-fragment-index="7">``Jaguar``: Indicator with 1=Jaguar and 0=otherwise.</li>
<li class="fragment fade-in" data-fragment-index="8">``BMW``: Indicator with 1=BMW and 0=otherwise.</li>
</ul>

## Data frame description

\bigskip
```{r, echo=F}
data("ThreeCars")
kable(head(ThreeCars), caption = "First five observations in the data")
```

# Plots of the variables

## Summary of the categorical variables

```{r, echo=F}
p1 = ggplot(data = ThreeCars, aes(x = CarType, y = Price, color = CarType)) +
  geom_boxplot() +
  theme_bw() +
  theme(legend.position = "none")

p2 = ggplot(data = ThreeCars, aes(x = CarType, y = Mileage, color = CarType)) +
  geom_boxplot() +
  theme_bw()

ggarrange(p1, p2, ncol = 2, widths = c(1, 1.4))
```

## Summary of the the numerical variables

```{r, echo=F}
bw1 = ks::hpi(ThreeCars$Price)
p1 = ggplot(data = ThreeCars, aes(x = Price)) +
  geom_histogram(binwidth = bw1, fill = "blue", color = "black") +
  theme_bw()

bw2 = ks::hpi(ThreeCars$Age)
p2 = ggplot(data = ThreeCars, aes(x = Age)) +
  geom_histogram(binwidth = bw2, fill = "orange", color = "black") +
  theme_bw()

p1 + p2
```

# Some insights

<ul>
<li class="fragment fade-in" data-fragment-index="1">From the **boxplots**, we can observe that the Porches are the most expensive cars, whereas the Jaguars have the cheapest mean, despite having a long range of values. Also, the BMW are the ones that have more kilometers.</li>

\bigskip
<li class="fragment fade-in" data-fragment-index="2"> From the **histograms**, we can see that the the price is right-skewed but it may have two modes around 30\$ and 50\$. On the other hand, the majority of cars are below than 10 years.</li>
</ul>

# Finally, a simple regression

We can make an interactive plot to see how related are the variables ``Price`` and ``Mileage``. As we may expect, as the km increases, the prices decreases.

```{r, eval=F}
fit <- lm(Price ~ Mileage, data = ThreeCars)
```

## 

```{r, echo=F}
fit <- lm(Price ~ Mileage, data = ThreeCars)

p <- ThreeCars %>%
  plot_ly(x = ~Mileage, color = ~CarType) %>%
  add_markers(y = ~Price) %>%
  add_lines(x = ~Mileage, y = fitted(fit))

htmlwidgets::saveWidget(p,'plotly.html')
knitr::include_url('plotly.html', height = "576px")
```

# THE END



